State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editted the abstract

\begin{abstract}
	This paper presents a framework for creating patient specific neural field models from electrophysiological data. A basis function decomposition of the Wilson and Cowen or Amari style neural field equations is used to form a state space model. Spatial frequency analysis methods are used for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field with the reduced finite dimensional model. Using the neural field model equation with modelled sensors, we generate data used to illustrate the state and parameter estimation framework. This framework provides a link between patient specific neurophysiological data and theoretical neural fields models. This link may lead to greater understanding of cortical dynamics at the meso and macroscopic scale where diseases such as epilepsy are manifested.   
\end{abstract}

>>>>

\begin{abstract}
	This paper presents a framework for creating patient-specific neural field models from electrophysiological data. The Wilson and Cowen or Amari style neural field equations are used as the parametric form of the model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using modelled sensors and the field model. We introduce a method to reduce the continuum neural field model, using a basis function decomposition, to form a finite dimensional state-space model to facilitate state and parameter estimation. Spatial frequency analysis methods are introduced for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field. The estimation process consists of a two stage algorithm, incorporating the unscented Rauch Tung Striebel Smoother for state estimation, and a least squares algorithm for parameter estimation. The results show that it is possible to reconstruct the neural field and estimate intracortical connectivity and synaptic time constant. The results illustrate the cost of the model reduction with a loss of the high spatial frequency information. This framework provides a link between patient specific neurophysiological data and theoretical neural fields models. This link may lead to greater understanding of cortical dynamics at the meso/macroscopic scale where diseases such as epilepsy are manifested.   
\end{abstract}
